---
title: "subgraph"
author: "Jackie Jiaqi Yin"
date: "4/17/2019"
output: 
        github_document:
                html_preview: true
---

```{r setup, include=FALSE}
<<<<<<< HEAD
knitr::opts_chunk$set(message=FALSE, warning=FALSE, autodep=TRUE)
```
## Overview
**subgraph** is a system for displaying graphs by showing the connected edges. You prvide the name of nodes, and the name of graph which is based on [the graph list](http://graphclasses.org/smallgraphs.html). Then **subgraph** will provide you all homogenous graphs by showing the connected edges. The maximum number of nodes is 6.
=======
knitr::opts_chunk$set(eval = FALSE, message=FALSE, warning=FALSE, autodep=TRUE)
```
## Overview
**subgraph** is a system for displaying graphs by showing the connected edges. Base on [the graph list](http://graphclasses.org/smallgraphs.html)
>>>>>>> b4ffae73821f545501986e35eafc53829fee9bf9


## Installation
```{r install}
# install.packages("devtools")
devtools::install_github("placeboo/subgraph")
<<<<<<< HEAD
install.packages("combinat", repos = "http://cran.us.r-project.org")
```


## Useage

```{r use}
library(subgraph)
library(combinat)
```
If we want to display all the possible homogenous graphs for [claw](http://graphclasses.org/images/g_claw.gif), whose number of nodes is 4,
```{r example}
claw(c(1:4))
```

## More
Check the help page. The package is incorporated with the working paper of mine.
=======
```

## Useage
```{r use}
library(subgraph)
```
>>>>>>> b4ffae73821f545501986e35eafc53829fee9bf9
